### 2024-07-22 NN/tables/backward.tex
commit

        \begin{table*}
            \centering
            \begin{tabular}{lr}
\hline
 features                                                                                                           &    R2 \\
\hline
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 76.09 \\
 ['conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 43.37 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 88.38 \\
 ['flow_rate1', 'conc_nano1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']    & 58.85 \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 67.6  \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2'] & 82.77 \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 57.26 \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 74.21 \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'heat_flux2', 'X_D2']    & 55.88 \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'X_D2']       & 64.76 \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2'] & 73.37 \\
 ['Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']                     & 83.52 \\
 ['flow_rate1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']                  & 67.85 \\
 ['flow_rate1', 'Kfluid1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']                     & 81.99 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']               & 74.67 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']                     & 83.17 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'Kfluid2', 'heat_flux2', 'X_D2']                     & 16.53 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'heat_flux2', 'X_D2']                  & 74.26 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'X_D2']                     & 66.81 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2']               & 69.09 \\
\hline
\end{tabular}
            \caption{Results of Backward Feature Elimination}
            \label{table-backward}
        \end{table*}

>>>>

        \begin{table*}
            \centering
            \begin{tabular}{lr}
\hline
 features                                                                                                                           &    R2 \\
\hline
 ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2'] & 82.69 \\
 ['conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2']                & 62.45 \\
 ['flow\_rate1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2']                & 81.63 \\
 ['flow\_rate1', 'conc\_nano1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2']            & 73.64 \\
 ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2']                & 72.94 \\
 ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2']          & 67.45 \\
 ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2']                & 68.03 \\
 ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'Kfluid2', 'heat\_flux2', 'X\_D2']                & 76.57 \\
 ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'heat\_flux2', 'X\_D2']            & 38.28 \\
 ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'X\_D2']                & 69.39 \\
 ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2']          & 81.61 \\
\hline
\end{tabular}
            \caption{Results of Backward Feature Elimination}
            \label{table-backward}
        \end{table*}

### 2024-07-22 NN/tables/forward.tex
commit

        \begin{table*}
            \centering
            \begin{tabular}{lr}
\hline
 features                                                            &     R2 \\
\hline
 ['X_D1']                                                            &  14.09 \\
 ['flow_rate2']                                                      &  38.24 \\
 ['conc_nano2']                                                      &  11.24 \\
 ['Kfluid2']                                                         &  62.95 \\
 ['heat_flux2']                                                      &   0.14 \\
 ['flow_rate1', 'Kfluid2']                                           &  63.47 \\
 ['conc_nano1', 'Kfluid2']                                           &  63.88 \\
 ['Kfluid1', 'Kfluid2']                                              &  62.25 \\
 ['heat_flux1', 'Kfluid2']                                           &  77.7  \\
 ['X_D1', 'Kfluid2']                                                 &  76.02 \\
 ['flow_rate2', 'Kfluid2']                                           & -31.69 \\
 ['conc_nano2', 'Kfluid2']                                           &  86.62 \\
 ['heat_flux2', 'Kfluid2']                                           &  76.09 \\
 ['X_D2', 'Kfluid2']                                                 &  78.17 \\
 ['flow_rate1', 'Kfluid2', 'conc_nano2']                             &  76.79 \\
 ['conc_nano1', 'Kfluid2', 'conc_nano2']                             &  87.83 \\
 ['Kfluid1', 'Kfluid2', 'conc_nano2']                                &  88.24 \\
 ['heat_flux1', 'Kfluid2', 'conc_nano2']                             &  91.58 \\
 ['X_D1', 'Kfluid2', 'conc_nano2']                                   &  82.59 \\
 ['flow_rate2', 'Kfluid2', 'conc_nano2']                             &  53.86 \\
 ['heat_flux2', 'Kfluid2', 'conc_nano2']                             &  75.43 \\
 ['X_D2', 'Kfluid2', 'conc_nano2']                                   &  64.89 \\
 ['flow_rate1', 'Kfluid2', 'conc_nano2', 'heat_flux1']               &  93.27 \\
 ['conc_nano1', 'Kfluid2', 'conc_nano2', 'heat_flux1']               &  76.38 \\
 ['Kfluid1', 'Kfluid2', 'conc_nano2', 'heat_flux1']                  &  92.71 \\
 ['X_D1', 'Kfluid2', 'conc_nano2', 'heat_flux1']                     &  86.97 \\
 ['flow_rate2', 'Kfluid2', 'conc_nano2', 'heat_flux1']               &  74.46 \\
 ['heat_flux2', 'Kfluid2', 'conc_nano2', 'heat_flux1']               &  81.11 \\
 ['X_D2', 'Kfluid2', 'conc_nano2', 'heat_flux1']                     &  63.44 \\
 ['conc_nano1', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1'] &  83.2  \\
 ['Kfluid1', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1']    &  66.6  \\
 ['X_D1', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1']       &  82.41 \\
 ['flow_rate2', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1'] &  49.69 \\
 ['heat_flux2', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1'] &  61.91 \\
 ['X_D2', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1']       &  70.43 \\
\hline
\end{tabular}
            \caption{Results of Forward Feature Selection for different features}
            \label{table-forward}
        \end{table*}

>>>>

        \begin{table*}
            \centering
            \begin{tabular}{lr}
\hline
 features                                                                           &    R2 \\
\hline
 ['X\_D1']                                                                          & 14.85 \\
 ['flow\_rate2']                                                                    & 27.69 \\
 ['conc\_nano2']                                                                    & 11.15 \\
 ['Kfluid2']                                                                        & 62.66 \\
 ['heat\_flux2']                                                                    & -4.92 \\
 ['flow\_rate1', 'Kfluid2']                                                         & 75.33 \\
 ['conc\_nano1', 'Kfluid2']                                                         & 64.49 \\
 ['Kfluid1', 'Kfluid2']                                                             & 67.9  \\
 ['heat\_flux1', 'Kfluid2']                                                         & 74.3  \\
 ['X\_D1', 'Kfluid2']                                                               & 67.3  \\
 ['flow\_rate2', 'Kfluid2']                                                         &  9.94 \\
 ['conc\_nano2', 'Kfluid2']                                                         & 87.59 \\
 ['heat\_flux2', 'Kfluid2']                                                         & 56.8  \\
 ['X\_D2', 'Kfluid2']                                                               & 67.59 \\
 ['flow\_rate1', 'Kfluid2', 'conc\_nano2']                                          & 60.42 \\
 ['conc\_nano1', 'Kfluid2', 'conc\_nano2']                                          & 78.36 \\
 ['Kfluid1', 'Kfluid2', 'conc\_nano2']                                              & 79.88 \\
 ['heat\_flux1', 'Kfluid2', 'conc\_nano2']                                          & 90.37 \\
 ['X\_D1', 'Kfluid2', 'conc\_nano2']                                                & 84.51 \\
 ['flow\_rate2', 'Kfluid2', 'conc\_nano2']                                          & 65.14 \\
 ['heat\_flux2', 'Kfluid2', 'conc\_nano2']                                          & 57.1  \\
 ['X\_D2', 'Kfluid2', 'conc\_nano2']                                                & 54.6  \\
 ['flow\_rate1', 'Kfluid2', 'conc\_nano2', 'heat\_flux1']                           & 62.62 \\
 ['conc\_nano1', 'Kfluid2', 'conc\_nano2', 'heat\_flux1']                           & 92.87 \\
 ['Kfluid1', 'Kfluid2', 'conc\_nano2', 'heat\_flux1']                               & 80.94 \\
 ['X\_D1', 'Kfluid2', 'conc\_nano2', 'heat\_flux1']                                 & 87.63 \\
 ['flow\_rate2', 'Kfluid2', 'conc\_nano2', 'heat\_flux1']                           & 82.76 \\
 ['heat\_flux2', 'Kfluid2', 'conc\_nano2', 'heat\_flux1']                           & 55.75 \\
 ['X\_D2', 'Kfluid2', 'conc\_nano2', 'heat\_flux1']                                 & 75.43 \\
 ['flow\_rate1', 'Kfluid2', 'conc\_nano2', 'heat\_flux1', 'conc\_nano1']            & 49.56 \\
 ['Kfluid1', 'Kfluid2', 'conc\_nano2', 'heat\_flux1', 'conc\_nano1']                & 93.06 \\
 ['X\_D1', 'Kfluid2', 'conc\_nano2', 'heat\_flux1', 'conc\_nano1']                  & 87.49 \\
 ['flow\_rate2', 'Kfluid2', 'conc\_nano2', 'heat\_flux1', 'conc\_nano1']            & 69.35 \\
 ['heat\_flux2', 'Kfluid2', 'conc\_nano2', 'heat\_flux1', 'conc\_nano1']            & 65.5  \\
 ['X\_D2', 'Kfluid2', 'conc\_nano2', 'heat\_flux1', 'conc\_nano1']                  & 64.18 \\
 ['flow\_rate1', 'Kfluid2', 'conc\_nano2', 'heat\_flux1', 'conc\_nano1', 'Kfluid1'] & 84.19 \\
 ['X\_D1', 'Kfluid2', 'conc\_nano2', 'heat\_flux1', 'conc\_nano1', 'Kfluid1']       & 87.54 \\
 ['flow\_rate2', 'Kfluid2', 'conc\_nano2', 'heat\_flux1', 'conc\_nano1', 'Kfluid1'] & 76.61 \\
 ['heat\_flux2', 'Kfluid2', 'conc\_nano2', 'heat\_flux1', 'conc\_nano1', 'Kfluid1'] & 71.81 \\
 ['X\_D2', 'Kfluid2', 'conc\_nano2', 'heat\_flux1', 'conc\_nano1', 'Kfluid1']       & 77.34 \\
\hline
\end{tabular}
            \caption{Results of Forward Feature Selection for different features}
            \label{table-forward}
        \end{table*}
